### 2017-02-08 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
writing 6b

\begin{theorem}

@@

%Pb
\subsection{b}
\begin{theorem}
There exists a tree $T' = (V,F)$ such that $d^T(u,v) \leq d^{T'}(u,v) \leq 4 d^T(u,v).$
\end{theorem}
\begin{proof}
Pick $v \in V$ with a parent $w \not \in V$ and contract edge $vw$ in $T$. Repeat until all nodes of $T$ are in $V$. Multiply by $4$ the weights on all remaining edges. Call the resulting tree $T'$. Note that clearly $d^{T'}(u,v) \leq 4d^T(u,v)$ as contracting only shortens the distances. Furthermore, in the worst case $d^{T'}(u,v) = 2^i \cdot 4$ if contraction results in contracting $u$ and $v$ right up to the cluster where they were separated (that is, contracting preserves the largest edge distance on the $uv$-path in $T$). But 
$$2^i \cdot 4 = 2^i + 2^i + 2^i + 2^i \geq d(S^u_{i-1}, S_i) + d(S^v_{i-1}, S_i) +  d(S^u_{i-1}, u) + d(S^v_{i-1}, v) = d^T(u,v).$$
Hence the theorem holds.
\end{proof}
\end{document}

>>>>

\begin{theorem}\label{th:tree-metric}

@@

%Pb
\subsection{b}
\paragraph{}
Let $G = (V,E)$ be a metric graph with edge costs $c:E \rightarrow \R_+$ and requirements $r(u,v) \in \N$ for all $u,v \in V$. We wish to operate on a tree with the same vertex set at $G$. The following theorem will let us do so.
\begin{theorem}
Let $T$ be a tree obtained by Theorem \ref{th:tree-metric}. Then there exists a tree $T' = (V,F)$ such that $d^T(u,v) \leq d^{T'}(u,v) \leq 4 d^T(u,v).$
\end{theorem}
\begin{proof}
Pick $v \in V$ with a parent $w \not \in V$ and contract edge $vw$ in $T$. Repeat until all nodes of $T$ are in $V$. Multiply by $4$ the weights on all remaining edges. Call the resulting tree $T'$. Note that clearly $d^{T'}(u,v) \leq 4d^T(u,v)$ as contracting only shortens the distances. Furthermore, in the worst case $d^{T'}(u,v) = 2^i \cdot 4$ if contraction results in contracting $u$ and $v$ right up to the cluster where they were separated (that is, contracting preserves the largest edge distance on the $uv$-path in $T$). But 
$$2^i \cdot 4 = 2^i + 2^i + 2^i + 2^i \geq d(S^u_{i-1}, S_i) + d(S^v_{i-1}, S_i) +  d(S^u_{i-1}, u) + d(S^v_{i-1}, v) = d^T(u,v).$$
Hence the theorem holds.
\end{proof}
\paragraph{}
Combining the above with Theorem \ref{th:tree-metric} and hiding the factor of $4$ in the $O$-notation we have the important corollary
\begin{corollary}\label{cor:tree-metric}
Let $G = (V,E)$ be a metric graph with edge lengths $d:E\rightarrow \R_+$ and $W \subset V$. One can randomly find a tree $T$ with vertex set $V$ such that
\begin{enumerate}
\item $d(u,v) \leq d^T(u,v)$ for all $u,v\in W$
\item $E[d^T(u,v)] \leq O(\log n) d(u,v)$ for all $u,v\in V$.
\end{enumerate}
\end{corollary}
\paragraph{}
Consider the following algorithm, $\cA$, for GSN on $G$:
\begin{enumerate}
\item Let $W = \{v \in V: \exists u \in V, r(u,v) > 0\}$.
\item Use Corollary \ref{cor:tree-metric} to compute a tree metric $T$ which approximates $G$ with $W$.
\item Solve GSN on $T$ and let $x$ be the resulting solution.
\item Return $x$.
\end{enumerate}
\paragraph{}
We want to show that $\cA$ is an $O(log |W|)$-approximation algorithm for GSN on $G$. Thus we need to show a few things:
\begin{enumerate}
\item That we can solve GSN on trees in polynomial time. This implies that $\cA$ runs in polynomial time since the tree of Theorem \ref{th:tree-metric} can be found in polynomial time, and the contractions necessary to yield the tree in Corollary \ref{cor:tree-metric} can be done in polynomial time. 
\item The $x$ returned is feasible on $G$.
\item The approximation factor holds.
\end{enumerate}
\paragraph{Proof of $1$}

\paragraph{Proof of $2$}

\paragraph{Proof of $3$}

\end{document}
